---
title: "Group 39 CA pollution burden"
author: "Sarah Lam and Anusha Sridhara"
date: "11/14/2021"
output: html_document
---

```{r setup, include= TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(janitor)
```

```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r, fig.cap = "The figure compares the CalEnviroScreen 3.0 score with the percentage of the census tract that is reported as white. The darker purple indicates a higher density of points on the figure.}
ggplot(data=ces, aes(x=white_percent, y=ces_3_0_score))+
  geom_hex() +
  labs(x = "Percent White Population of Census Tract",
       y = "CalEnviroScreen 3.0 Score",
       title = "CalEnviroScreen 3.0 Score by White Population Demographic")+ 
       scale_fill_gradient(low= "darkorchid1", high="darkorchid4")+
  theme_minimal()
```
The graph indicates that on average, a higher percentage of white population (approx 75%) is less affected by pollution as indicated by the CalEnviroScreen 3.0 Score of less than 25. This also suggests that there exists a negative correlation between percentage of white population and potential exposure to pollution. 

Citations:

Office of Environmental Health and Hazard Assessment, CalEnviroScreen 3.0 Demographics (Jun. 2018), https://oehha.ca.gov/calenviroscreen/report/calenviroscreen-30


